\section*{Teaching}

I enjoy teaching, and very much appreciate its importance for doing research.
In addition to solidifying my own understanding of the material, teaching a topic is also a wonderful exercise in communication.
After all, the most novel of ideas is useless unless you can communicate it effectively.

\paragraph{Teaching Assistant}
\label{par:teaching_assistant}
My first experience teaching a class was in sophomore year, when I was a TA for the second level undergraduate algorithms course.
This also happened to be the semester when the course was being recorded for MIT Open Courseware.
So, my videos of my recitation were going to be recorded, and posted on the OCW website (recitations $\{2,6,8,9\}$
\href{https://ocw.mit.edu/courses/electrical-engineering-and-computer-science/6-046j-design-and-analysis-of-algorithms-spring-2015/recitation-videos/}{available online}).

Since this was my first teaching experience, I spent a long time preparing for each recitation,
and I thoroughly enjoyed the process of preparing material, and teaching a class.
I have since been a TA for this class three times, and I have solidified my understanding further everytime.

\paragraph{Independent Teaching}
\label{par:independent_teaching}
I have also undertaken several independent teaching related activities.
During my Junior year, I designed, and taught a month-long algorithms course at MIT, with 40 students.
Last summer (2017), I started a workshop for high school students in my hometown in India.
During this three-week intensive workshop, the participants learned C programming,
basic simulations, and completed a hands-on robotics project.
